%________________________________________________________________________________________
\documentclass[margin,line]{resume}
%\usepackage[pdftex,colorlinks=true,urlcolor=blue]{hyperref}
\usepackage[ocgcolorlinks,urlcolor=blue]{hyperref}
\begin{document}
\name{\Large David Trowbridge}
\begin{resume}


    %____________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    27766 Stirrup Way \hfill (650) 996-5273\\
    Los Altos Hills, CA 94022 \hfill \href{mailto:trowbrds@gmail.com}{trowbrds@gmail.com}\\
    \hspace*{0pt} \hfill \href{https://github.com/davidt}{https://github.com/davidt}

%    \begin{tabular}{@{} l @{\hspace{69mm}} r}
%    27766 Stirrup Way         & (650) 996-5273                                              \\
%    Los Altos Hills, CA 94022 & \href{mailto:trowbrds@gmail.com}{trowbrds@gmail.com}        \\
%                              & \href{https://github.com/davidt}{https://github.com/davidt} \\
%    \end{tabular}

    %____________________________________________________________________________________
    % Qualifications and Interests
    \section{\mysidestyle Qualifications\\and Interests}

    \begin{list2}
        \item Keen interest and experience in web-based and desktop
              applications, including user interface design and development.
        \item Extensive experience with C, C++, Python, HTML5/Javascript/CSS,
              and Go, and familiarity with many other environments and
              languages.
        \item Expert knowledge of building applications using Django (for the
              web) and GTK+/GNOME (for the Linux desktop).
        \item Broad experience working with the open-source community and a
              thorough understanding of software licensing issues.
        \item Ability to adapt quickly to new situations and environments.
        \item Proven experience shipping large, high quality software projects
              on schedule.
    \end{list2}


    %____________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\and Open Source\\Experience}
    {\bf VMware, Inc.}, Palo Alto, California \vspace{2mm}\\\vspace{1mm}%
    {\sl Staff Engineer/Engineering Lead} \hfill {\bf August 2006 -- present}\\
    At VMware, I have helped build and ship several major products as a Linux
    user interface developer on the Workstation/Player team.
    \vspace{3mm}
    \begin{list2}
    \item Responsible for the conception, design, and implementation of several
          major features for Workstation and Player on Linux. Examples include
          ``Workstation as a Server'' and remote connectivity features in
          Workstation 8.0, Encrypted VMs in Workstation 7.0, and Record/Replay
          in 6.5.
    \item Organized and coordinated cross-functional teams, working with people
          across different business units to align goals across major product
          lines.
    \item Set schedules, organized smaller feature teams, and guided various
          releases through completion. These activities were formalized for the
          7.0 and 8.0 releases, where I acted as Tech Lead.
    \item Developed, evangelized and instituted several improvements to software
          development process and infrastructure, including the adoption of
          Review Board for code review, and a set of tools and procedures for
          using Git on top of Perforce for local development.
    \item Mediated conflicts between members of my team and other groups
          including product management and QA, as well as between my peers and
          management.
    \item Mentored several interns and junior employees throughout my tenure.
    \end{list2}

    {\bf Review Board}, \href{http://www.reviewboard.org}{http://www.reviewboard.org} \vspace{2mm}\\\vspace{1mm}%
    {\sl Founder, Maintainer} \hfill {\bf January 2007 -- present}\\
    Review Board is a web-based tool for collaborative code review. Christian
    Hammond and I started Review Board in order to create a tool which would
    satisfy our needs both in the open source world, as well as handle the
    challenge of maintaining a rigorous code review process in a quickly growing
    team at VMware. It supports many revision control systems and provides a
    powerful diff viewer with direct, in-line commenting.

    Review Board is now a mature open source project with a large community. It
    is used by thousands of companies and open-source projects, including
    VMware, Yahoo!, Twitter, and Asterisk, and has had received contributions
    from over 200 people.

    {\bf Student Mentorship}\hfill{\bf 2008 -- present}\vspace{2mm}\\
    Review Board has participated several times as a mentoring organization in
    Google's Summer of Code program
    (\href{http://code.google.com/soc}{http://code.google.com/soc})
    and the Undergraduate Capstone Open Source Projects program
    (\href{http://www.ucosp.ca}{http://www.ucosp.ca}). I have mentored nearly
    fifty students from top universities, teaching ``real-world'' software
    development practices.

    \newpage

    {\bf Beanbag, Inc.}, Palo Alto, California \vspace{2mm}\\\vspace{1mm}%
    {\sl Founder} \hfill {\bf November 2010 -- present }\\
    Beanbag, Inc. is a business founded to support the open-source Review Board
    project. My efforts are currently focused on enabling the use of Review
    Board as a subscription service.
    \vspace{3mm}
    \begin{list2}
    \item Built, supported, and advertised \href{http://rbcommons.com}{RBCommons.com},
          and grew sales to make Beanbag, Inc. a profitable company.
    \item Added secure, multi-tenant hosting capabilities on top of the open
          source version of Review Board.
    \item Helped with design and implementation of ``sponsored'' features for
          Review Board.
    \item Managed administrative aspects of the business, including accounting
          and finance.
    \end{list2}

    {\bf XChat-GNOME}, \href{https://live.gnome.org/Xchat-Gnome}{https://live.gnome.org/Xchat-Gnome} \vspace{2mm}\\\vspace{1mm}%
    {\sl Founder, Maintainer} \hfill {\bf 2004 -- 2007}\\
    XChat-GNOME was a new front-end to the popular ``Xchat'' IRC client, with an
    emphasis on ease of use, simplicity and desktop integration. I created
    XChat-GNOME because I was dissatisfied with all of the existing clients,
    which burdened users with extensive configuration, steep learning curves,
    and cluttered user interfaces. In 2007, I passed off maintenance of
    XChat-GNOME to other members of the GNOME community.

    {\bf Fyre}, \href{http://fyre.navi.cx}{http://fyre.navi.cx} \vspace{2mm}\\\vspace{1mm}%
    {\sl Founder, Maintainer} \hfill {\bf 2003 -- 2006}\\
    Fyre is a software system to produce computational art from chaotic maps
    with advanced features such as animation and cluster rendering. One of the
    algorithms developed for Fyre won first place in the undergraduate division
    of the ACM student research competition at SIGGRAPH 2004.

    \ifcv
        {\bf BZFlag}, \href{http://www.bzflag.org}{http://www.bzflag.org} \vspace{2mm}\\\vspace{1mm}%
        {\sl Core Developer} \hfill {\bf 2000 -- 2006}\\
        BZFlag is an online, 3D multiplayer action game which runs on over a dozen
        different platforms. It is one of the most popular games ever on Silicon
        Graphics (sgi) machines. My contributions include large architecture changes
        during the 1.8/1.9 development cycle, assistance with developing a new
        rendering engine and many other small features, as well as several versions
        of a WYSIWYG linux map editor named “bzedit” from 2000-2003.

        {\bf University of Colorado}, Boulder, Colorado \vspace{2mm}\\\vspace{1mm}%
        {\sl Student Systems Administrator for ``CSops''} \hfill {\bf August 2002 -- July 2006}\\
        System and network administration, and support of a large conference
        center. This included administration of OpenBSD and Linux servers, as well
        as Linux and Solaris-based student labs. My network administration duties
        involved maintaining routing tables and 802.1q network topologies on a
        variety of network hardware. The conference center support role focused
        mostly on documentation and troubleshooting of a multimillion-dollar
        audio/video setup, including complex switching and control equipment.

        {\bf University of Colorado}, Boulder, Colorado \vspace{2mm}\\\vspace{1mm}%
        {\sl Research Assistant} \hfill {\bf January 2005 -- June 2006}\\
        As an undergraduate research assistant, I participated in a research
        project dealing with analysis of motion capture data. I built software to
        create probability graphs (similar to markov chains) from a continuous
        motion sequence, and then walked those graphs using chaotic mathematical
        systems, with the goal of creating stylistically consonant interpolations
        between poses in the context of dance choreography.

        {\bf Evolution}, \href{http://gnome.org/projects/evolution}{http://gnome.org/projects/evolution} \vspace{2mm}\\\vspace{1mm}%
        {\sl Contributor} \hfill {\bf 2003 -- 2005}\\
        Evolution is a popular application for the GNOME desktop which provides
        E-mail, addressbook and calendaring features. My particular contributions
        include calendar publishing, weather calendars and updates to the
        documentation. These contributions were made as part of the GNOME bounties
        program sponsored by Novell.

        {\bf SGI Federal, Inc.}, Englewood, Colorado \vspace{2mm}\\\vspace{1mm}%
        {\sl Intern} \hfill {\bf June 2004 -- August 2004}\\
        At sgi, I ported customer software from IRIX/MIPS to Linux/Itanium2, and
        worked on integration of chromium (the open-source analog to sgi's OpenGL
        Multipipe) with SGI visualization systems. I also contributed to
        performance analysis and benchmarking of database systems on various SGI
        Altix configurations.

        {\bf Niwot Networks}, Boulder, Colorado \vspace{2mm}\\\vspace{1mm}%
        {\sl Intern} \hfill {\bf May 2001 -- September 2001}\\
        As a summer intern, I began work on creating a Linux server for Niwot
        Networks' high-performance file transfer software {\sl Gigabyte Express}.

        {\bf SignalSoft}, Boulder, Colorado \vspace{2mm}\\\vspace{1mm}%
        {\sl Intern} \hfill {\bf June 2000 -- January 2001}\\
        At SignalSoft, an early mobile location-based services company, I built a
        variety of web-site back-end scripts for customer interaction and intranet
        automation. I also created applications for remote testing of WAP
        (wireless application protocol) content servers for use prior to customer
        and partner demos.
    \fi

    %____________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    {\bf University of Colorado}, Boulder, Colorado. May 2006 \vspace{2mm}%
    \begin{list2}
    \item[] Bachelor of Science, Computer Science
    \item[] Bachelor of Arts, Music
    \end{list2}
    \ifcv
        {\bf Fairview High School}, Boulder, Colorado. June 2001 \vspace{2mm}%
        \begin{list2}
        \item[] Graduated with Honors
        \end{list2}
    \fi

    %____________________________________________________________________________________
    % Patents, Papers and Talks
    \ifcv
        \section{\mysidestyle Patents, Papers, and Talks}
    \else
        \section{\mysidestyle Patents and Papers}
    \fi

    {\bf``Graphical User Interface for Managing Virtual Machines''}{\it (patent pending)} \vspace{2mm}\\
    This patent application is for a particular combination of marking
    items as favorite, organization, and search capabilities, which combine
    to dramatically improve the user experience when managing large numbers
    of virtual machines.

    {\bf``Real-time Histogram Imaging''} \vspace{2mm}\\
    This work was presented as a poster at SIGGRAPH 2004, winning first place in
    the undergraduate division of the ACM/SIGGRAPH student research competition.
    This paper is based on that work, and was the entry to the 2004-2005 ACM
    student research competition grand finals. Available in the ACM digital
    library and at \href{http://bit.ly/WpwHEt}{http://bit.ly/WpwHEt}

    \ifcv
        {\bf``Developing Review Board''} \vspace{2mm}\\
        Talk on the challenges of redistributable webapps, and some specific
        technologies in Review Board. Presented at DjangoCon 2008. Slides
        available at \href{http://bit.ly/90Q76c}{http://bit.ly/90Q76c}
    \fi

    \ifcv
        \newpage
    \fi

    %____________________________________________________________________________________
    % Other Achievements
    \section{\mysidestyle Other Achievements}

    \begin{list2}
    \item Third degree black belt in American Kenpo and volunteer senior instructor
          at the Stanford Kenpo Karate Association.
    \item Numerous recognition awards at VMware, including winning an internal
          innovation contest and a business-unit wide ``making a difference''
          award (nominated by peers).
    \ifcv
        \item 'Cellist in the Longmont Symphony Orchestra during the 2000-2001
              season and the University of Colorado Symphony Orchestra from 2001
              to 2004.
    \fi
    \end{list2}


    \ifcv
    \else
        %____________________________________________________________________________________
        % Misc
        \section{}
        {\sl Further detail, older employment, additional open-source work, and references
             available upon request.}
    \fi


%________________________________________________________________________________________
\end{resume}
\end{document}

%________________________________________________________________________________________
% EOF

% vim: sw=4 ts=4 expandtab
